A subjective Bayesian framework for synthesizing deep uncertainties in climate risk management

### 2022-09-29 papers/earths-future/reviewer_response_01.tex

    Overall, I found the work well written and informative, and I think it is very promising.
    The framework's novelty arises from the way it stitches standard methods from Bayesian statistics and DMDU.
    This is not a negative statement, as I think by employing common-sense methods in a novel way the authors' framework is more likely to gain traction.
    An important contribution is the introduction, which nicely lays out the current state of practice, emerging methods (primarily from the DMDU community), and then research gaps.
    I appreciated the author's care in discussing the difficulty in adopting non-stationary frequency methods for extremes, with key citations to important works by Montanari, Seranaldi, and Bulletin 17C's introduction.
}

\AR{
    Thank you for your comments.
    This is an excellent summary of the aim and scope of this paper.
}

\RC{
    The use of the word model to mean different things. Throughout the manuscript, and particularly in Figure 1, the authors utilize the term `model' to refer to both the combination of RCP-SLR model/assumption and the systems model.
    I found this confusing at multiple places.
    One suggestion is to call the 'models' in box d of Figure 1 'scenarios' or something like that.
    So the scenario is the deep uncertainty (RCP-SLR model) and then the possible futures in box b of Figure 1 are samples drawn from the pdf that's conditioned on the scenario in Box d.
    I think this new terminology would be particularly important if one were to have more than one systems model in box c.
}

\AR{
    Thank you for flagging this as an opportunity to improve clarity.
    After some discussion we have decided to refer to ``scenarios'' (where it adds clarity, ``probabilistic scenarios'') and ``models'' (or ``physical models'' where it is helpful to draw distinctions from, \eg, system models).
}

@@

\RC{
    I understand the intention of the paper is to showcase the method, not necessarily the results.
    This said, some more discussion about the findings would be helpful.
    For example, in Figure 7A there is a spike after 0 ft of increased height. If some detail were given on the construction cost function (taken from another work), and at least a few more sentences on the results, I think it would really improve an already very good manuscript.
}

\AR{
    Good suggestion, can do.
}

\begin{quote}
    Copy and paste in the new text where we discuss figure 7A
\end{quote}
